A Heuristic Coconut-based Algorithm

### 2022-11-26 paper.tex
Magic thing for the fonts to render correctly in the paper.
Added some references that I'll probably use and some notes from one I'm sort of reading

@@

\section{Introduction}
Write a fancy paper here\cite{Kocher2018spectre}.
\section{Background}
Talk about how awesome the topic is.
\section{Related Work}
Explain the three papers.
\section{Future Work}
Say what could we build from here.
\section{Conclusion}
Summarize and incite.

>>>>

\usepackage[T1]{fontenc}

@@

\section{Introduction}
Write a fancy paper here\cite{mosier2022}.
\section{Background}
Talk about how awesome the topic is.
\section{Related Work}
Explain the three papers.\cite{canella2019} \cite{cats2022}
\section{Future Work}
Say what could we build from here.
\section{Conclusion}
Summarize and incite.

Shepard, Brookes, and Denz \cite{shepherd2022transient} mention power consumption and EM radiation as potential side channels.
Could be sad sad how to axiomatic model \emph{all} side effects.
They also brought my attention to the fact that cache by itself presents a side channel with or without speculative execution.
Since caching can affect access speed in either case, a sufficiently precise timer can detect which cache lines have been recently touched and from there make inferences about values.
This is possible because addresses are the same thing as data - one can use data as an address and thereby affect cache state in a manner directly correlated to the data value.

Something about optimize for the common case.
Transient execution exploits the edges.
Can coin flips provide security and an acceptable performance?
Complicated machinery in processors to make predictions, throw predictions out and take an 80\% hit to performance.
But, replace them with highly/suffficiently rng, and make coin-flip predictions - 50\% of the time they're right every time?
Adds a ton of noise to the side channels, how much does it really affect performance from a non-speculative baseline or from the super advanced but exploitable current gen?

Lawl, I don't really want to pursue that, do I?
Would be hilarious, I think.
